
# PubMed


thank you for your interest in using our software!
In your case you will mainly want to focus on working with the R-backend. It requires installation of a range of R-packages, which are listed here https://github.com/OpenKnowledgeMaps/Headstart/blob/master/doc/server_config.md

The scripts that execute our analytics workflow are located in "server/preprocessing/other-scripts/".
For an example of how it works, please have a look at the pubmed-test.R script in the test folders. The main data structure that you want to manipulate if you want to work with larger datasets is input_data.
You can change the search parameters (date range, document types) in params_pubmed.json, the search term with the "query" parameter, and especially remove the limit of 100 documents by changing "input_data = get_papers(query, params, limit=NNN)".

After that, you should be able to create the output_json as usual - you may want to relax the MAX_CLUSTERS parameter as well.



currently, our docker images are out-of-date. We are working on new versions of them, but in the meantime, I can propose another method.
You can run a local example, with your own data by adapting the local_files example described in the README under the "Getting started" example https://github.com/OpenKnowledgeMaps/Headstart/blob/master/README.md

1) Prepare and deploy the client, as described in https://github.com/OpenKnowledgeMaps/Headstart/blob/master/doc/README.md#deploying-the-client
2) verify that the local_files example works as described
3) You can then start working on your own examples by producing your own csv files to replace the example files - please compare the data and folder structure in the examples/local_files folder with your browser view to get a better understanding. You can create the CSV files as output from the R backend as described in last email.
4) You then need to adapt the local_files/data-config.js to load your own CSVs
5) After starting the local server you should be able to visualize your results



the sequence of the getting input data and creating the map data can be found in the example of https://github.com/OpenKnowledgeMaps/Headstart/blob/master/server/preprocessing/other-scripts/test/pubmed-test.R
if you refer to the  workflow of creating map data from input data, that specific workflow is in https://github.com/OpenKnowledgeMaps/Headstart/blob/master/server/preprocessing/other-scripts/vis_layout.R


```{r}
source("R/test/pubmed-test.R")

```



```{r}
source("R/vis_layout.R")

```







```{r utils, include=FALSE}
source(file = here::here("R/utils.R"))
```



```{r preprocess, include=FALSE}
source(file = here::here("R", "preprocess.R"))
```




```{r features, include=FALSE}
source(file = here::here("R", "features.R"))
```



```{r cluster, include=FALSE}
source(file = here::here("R", "cluster.R"))
```




```{r summarize, include=FALSE}
source(file = here::here("R", "summarize.R"))
```





```{r postprocess, include=FALSE}
source(file = here::here("R", "postprocess.R"))
```





```{r vis_layout, include=FALSE}
source(file = here::here("R", "vis_layout.R"))
```





```{r pubmed, include=FALSE}
source(file = here::here("R", "pubmed.R"))
```





```{r pubmed-test, include=FALSE}
source(file = here::here("R", "pubmed-test.R"))
```


---


# base



```{r base, include=FALSE}
source(file = here::here("R", "base.R"))
```




```{r base-test-ger, include=FALSE}
source(file = here::here("R", "base-test-ger.R"))
```




```{r base-test, include=FALSE}
source(file = here::here("R", "base-test.R"))
```




---


# altmetrics


```{r altmetrics, include=FALSE}
source(file = here::here("R", "altmetrics.R"))
```

---

# doaj


```{r doaj, include=FALSE}
source(file = here::here("R", "doaj.R"))
```




```{r doaj-test, include=FALSE}
source(file = here::here("R", "doaj-test.R"))
```



---

# linked category


```{r linkedcat, include=FALSE}
source(file = here::here("R", "linkedcat.R"))
```




```{r linkedcat-test, include=FALSE}
source(file = here::here("R", "linkedcat-test.R"))
```



## author view

```{r linkedcat_authorview, include=FALSE}
source(file = here::here("R", "linkedcat_authorview.R"))
```




```{r linkedcat_authorview-test, include=FALSE}
source(file = here::here("R", "linkedcat_authorview-test.R"))
```



## browse view


```{r linkedcat_browseview, include=FALSE}
source(file = here::here("R", "linkedcat_browseview.R"))
```


```{r linkedcat_browseview-test, include=FALSE}
source(file = here::here("R", "linkedcat_browseview-test.R"))
```



# openaire

```{r openaire, include=FALSE}
source(file = here::here("R", "openaire.R"))
```


```{r test-openaire, include=FALSE}
source(file = here::here("R", "test-openaire.R"))
```


# rplos


```{r rplos, include=FALSE}
source(file = here::here("R", "rplos.R"))
```



```{r rplos_fast, include=FALSE}
source(file = here::here("R", "rplos_fast.R"))
```


```{r rplos_fast-test, include=FALSE}
source(file = here::here("R", "rplos_fast-test.R"))
```



# cluster

```{r scaling_clustering, include=FALSE}
source(file = here::here("R", "scaling_clustering.R"))
```


# streamgraph

```{r streamgraph, include=FALSE}
source(file = here::here("R", "streamgraph.R"))
```



# snapshot



```{r create_snapshots, include=FALSE}
source(file = here::here("R", "create_snapshots.R"))
```


```{r validate_base_snapshots, include=FALSE}
source(file = here::here("R", "validate_base_snapshots.R"))
```




```{r validate_pubmed_snapshots, include=FALSE}
source(file = here::here("R", "validate_pubmed_snapshots.R"))
```





# curl


```{r curl_test, include=FALSE}
source(file = here::here("R", "curl_test.R"))
```






# similarity





```{r text_similarity, include=FALSE}
source(file = here::here("R", "text_similarity.R"))
```







openaire.R
altmetrics.R
base.R
cluster.R
doaj.R
features.R
linkedcat_authorview.R
linkedcat_browseview.R
linkedcat.R
postprocess.R
preprocess.R
pubmed.R
rplos_fast.R
rplos.R
run_vis_layout.R
scaling_clustering.r
streamgraph.R
summarize.R
test
text_similarity.R
utils.R
vis_layout.R

